---
title: "Distance Analysis Report"
output: html_document
date: "2022-07-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('npdr_external_dist.R')
```

# 10% Main Variable
```{r, Data 1,include=FALSE}
```

## Data Generation
```{r, Simulate Data,echo=FALSE}
```

## npdr
```{r, npdr,echo=FALSE}
```

## Autoencoder
```{r, Autoencoder,echo=FALSE}
```

## Random Forrest
```{r, Random Forrest,echo=FALSE}
```

## Principal Components
```{r, Principal Components,echo=FALSE}
```

## Evaluation Metrics
```{r, Evaluation Metrics,echo=FALSE}
```

``` {r}
Eval1 <- Results
```





# 25% Main Variable
```{r, Data 2,include=FALSE}
```

## Data Generation
```{r, Simulate Data,echo=FALSE}
```

## npdr
```{r, npdr,echo=FALSE}
```

## Autoencoder
```{r, Autoencoder,echo=FALSE}
```

## Random Forrest
```{r, Random Forrest,echo=FALSE}
```

## Principal Components
```{r, Principal Components,echo=FALSE}
```

## Evaluation Metrics
```{r, Evaluation Metrics,echo=FALSE}
```

``` {r}
Eval2 <- Results
```


# 50% Main Variable
```{r, Data 3,include=FALSE}
```

## Data Generation
```{r, Simulate Data,echo=FALSE}
```

## npdr
```{r, npdr,echo=FALSE}
```

## Autoencoder
```{r, Autoencoder,echo=FALSE}
```

## Random Forrest
```{r, Random Forrest,echo=FALSE}
```

## Principal Components
```{r, Principal Components,echo=FALSE}
```

## Evaluation Metrics
```{r, Evaluation Metrics,echo=FALSE}
```

``` {r}
Eval3 <- Results
```





# 75% Main Variable
```{r, Data 4,include=FALSE}
```

## Data Generation
```{r, Simulate Data,echo=FALSE}
```

## npdr
```{r, npdr,echo=FALSE}
```

## Autoencoder
```{r, Autoencoder,echo=FALSE}
```

## Random Forrest
```{r, Random Forrest,echo=FALSE}
```

## Principal Components
```{r, Principal Components,echo=FALSE}
```

## Evaluation Metrics
```{r, Evaluation Metrics,echo=FALSE}
```

``` {r}
Eval4 <- Results
```


# 90% Main Variable
```{r, Data 5,include=FALSE}
```

## Data Generation
```{r, Simulate Data,echo=FALSE}
```

## npdr
```{r, npdr,echo=FALSE}
```

## Autoencoder
```{r, Autoencoder,echo=FALSE}
```

## Random Forrest
```{r, Random Forrest,echo=FALSE}
```

## Principal Components
```{r, Principal Components,echo=FALSE}
```

## Evaluation Metrics
```{r, Evaluation Metrics,echo=FALSE}
```

``` {r}
Eval5 <- Results
```


# Results
## 10%
``` {r, echo=FALSE}
print(Eval1)
```
## 25%
``` {r, echo=FALSE}
print(Eval2)
```
## 50%
``` {r, echo=FALSE}
print(Eval3)
```
## 75%
``` {r, echo=FALSE}
print(Eval4)
```
## 90%
``` {r, echo=FALSE}
print(Eval5)
```
